\documentclass[11pt,a4paper]{article}

% ---------- Packages ----------
\usepackage[left=1.4cm, right=1.4cm, top=1.2cm, bottom=1.2cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{fontawesome5}

\setlength{\parindent}{0pt}
\pagenumbering{gobble}

% ---------- Colors ----------
\definecolor{heading}{RGB}{128,128,128}
\definecolor{subheading}{RGB}{90,90,90}

% ---------- Section Style ----------
\titleformat{\section}{
  \large\bfseries\color{heading}
}{}{0em}{}[\titlerule]

\titlespacing*{\section}{0pt}{6pt}{4pt} 

% ---------- Custom Commands ----------
\newcommand{\resumeItem}[1]{
  \item \small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \textbf{#1} \hfill \textit{#2} \\
  \textit{#3} \hfill \textit{#4}
}

% ---------- Document ----------
\begin{document}

% ---------- Header ----------
{\LARGE \textbf{Haoran Chen}} \\[2pt]
\textit{Software Engineer \& Data Engineer — Python / ETL / Data Analytics / C++} \\[4pt]
Munich, Germany \quad|\quad EU Work Permit \quad|\quad +49 178 6047880 \quad|\quad haoran.chen.job@outlook.com \\[2pt]
GitHub: github.com/haoran-chen \quad|\quad LinkedIn: linkedin.com/in/haoran-chen

\vspace{2pt}

% ---------- Summary ----------
\section*{Summary}
Software and Data Engineer with 4+ years of experience building scalable data pipelines, ETL processes, and robust backend architectures using Python and C++. Proven track record in processing complex datasets, designing observability dashboards for KPI monitoring, and modernizing legacy database models. Passionate about enabling data-driven decision-making, working within agile environments, and continuously expanding cloud infrastructure expertise (AWS/Azure). Adept at collaborating with cross-functional stakeholders to translate business requirements into impactful analytical solutions.

\vspace{2pt}

% ---------- Professional Experience ----------
\section*{Professional Experience}

\resumeSubheading{Planet Protel Hotelsoftware GmbH}{Oct 2024 -- Present}{Software Engineer (Data Architecture \& C++)}{Germany}
\begin{itemize}[leftmargin=*, parsep=0pt, itemsep=2pt, topsep=2pt]
  \resumeItem{Collaborated with cross-functional teams (Product, QA, Operations) to gather requirements and translate business needs into robust data architectures and working code.}
  \resumeItem{Refactored and optimized legacy data models and complex database queries (MSSQL) to improve performance, reporting accuracy, and data consistency for global Enterprise clients.}
  \resumeItem{Engineered an atomic DataChangeLog architecture to ensure strict audit trails and financial compliance.}
  \resumeItem{Modernized core on-premise components, ensuring seamless data integration and long-term stability during hybrid cloud transitions.}
\end{itemize}

\vspace{2pt}

\resumeSubheading{Bertrandt Engineering Office GmbH}{Apr 2022 -- Jul 2024}{Software Developer (Data Pipelines \& Python)}{Germany}
\begin{itemize}[leftmargin=*, parsep=0pt, itemsep=2pt, topsep=2pt]
  \resumeItem{Developed and optimized robust ETL data pipelines using Python (FastAPI, Pandas), Apache Airflow, and C++ to process and analyze large-scale vehicle-recorded data.}
  \resumeItem{Designed and implemented data visualization dashboards (Grafana, InfluxDB) for KPI monitoring and data observability, enabling stakeholders to rapidly identify trends and make data-driven decisions.}
  \resumeItem{Implemented automated testing and mocking strategies to improve the reliability and maintainability of core analytical systems.}
  \resumeItem{Actively participated in agile development cycles (Scrum), consistently iterating approaches based on new data insights and evolving client requirements.}
\end{itemize}

\vspace{2pt}

\resumeSubheading{Forschungszentrum J\"ulich}{Oct 2021 -- May 2022}{Master Thesis (Data Analysis \& HPC)}{Germany}
\begin{itemize}[leftmargin=*, parsep=0pt, itemsep=2pt, topsep=2pt]
  \resumeItem{Implemented complex mathematical models and data analysis pipelines using Python (SciPy, NumPy) to analyze and visualize massive datasets from active filament systems.}
  \resumeItem{Utilized distributed computing techniques and OpenMP on High-Performance Computing (HPC) clusters (Linux) for large-scale stochastic simulations.}
\end{itemize}

\vspace{2pt}

% ---------- Technical Skills ----------
\section*{Technical Skills}

\textbf{Data Engineering \& Analytics:} Python (Pandas, SciPy, FastAPI), ETL Processes, Apache Airflow, Data Modeling \\
\textbf{Databases \& Cloud Computing:} MSSQL, SQLite, Cloud Concepts (AWS/Azure), Distributed Computing \\
\textbf{Visualization \& Front-end:} Grafana, InfluxDB, PowerBI Concepts, HTML/CSS/JavaScript (Basic) \\
\textbf{Core Software Engineering:} C++, Docker, CI/CD pipelines, Multithreading, Agile/Scrum Methodologies

\vspace{2pt}

% ---------- Education ----------
\section*{Education}

\resumeSubheading{RWTH Aachen University}{2019 -- 2022}{Master of Science -- Material Science}{Aachen, Germany}
\begin{itemize}[leftmargin=*, parsep=0pt, itemsep=2pt, topsep=2pt]
  \resumeItem{\textit{Thesis:} Brownian Dynamics Simulations of Dense Active Filament Systems (Focus on Data Analytics \& HPC)}
\end{itemize}

\vspace{2pt}

\resumeSubheading{University of Science and Technology Beijing}{2013 -- 2017}{Bachelor of Engineering -- Nanomaterials and Nanotechnology}{Beijing, China}

\end{document}